koda: Deep Learning-Enhanced Pipeline for Keyword Detection in Document Images

### 2020-01-15 paper/paper.tex
Add TOC

\begin{abstract}
This paper proposes a pipeline, KODA, suitable for keyword highlighting in document images. At its core, KODA uses a combination of edge detection, hough transform, OCR and warping to achieve the result. 
We describe the custom, deep learning-based, approach for edge detection, motivated by the problems of traditional techniques and explaining the model training process, along with examples.
We then describe the document detection and warping algorithms, as well as the keyword highlighting process.
\end{abstract}

@@

The process is divided into two macro tasks (shown in Fig. \ref{fig:pipeline}): corners detection and document analysis. The formers takes as input a generic image containing a document and returns the 2D coordinates of its corners. The latter use the corners coordinates to warp the image, apply an OCR to read the document words and returns the original and warped image with the highlighted keywords specified by the user. Considering KODA as a black box, the user loads an image and, for each keyword specified, retrieves a copy of the image containing the highlighted word.

\begin{figure}[!htbp]
	\includegraphics[width=\linewidth]{ipt.png}
	\caption{Image processing tasks example. Note: edges detection returns a resized (256x256)}
	\label{fig:imageprocessing}
\end{figure}

\begin{figure}[!htbp]
	\includegraphics[width=\linewidth]{Pipeline.png}
	\caption{KODA Pipeline scheme with sub-tasks. The computationally expensive processing is done once per input image, then the user can search for keywords and retrieves the output image multiple times repeatedly.}
	\label{fig:pipeline}
\end{figure}

@@

\subsection{First Attempts with Canny}

@@

\subsection{Deep Learning Approach}

@@

@@

Once a set of lines is found, a sub-task is responsible to select the four best ones, one per each document edge. This is accomplished exploiting the fact that the Hough lines returned by the OpenCV interface are ordered by confidence: the first four strongest ones are selected.

\begin{figure}[H]
	\makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{Hough.png}}
	\caption{TODO}
	\label{fig:hough}
\end{figure}

@@

Once the four Hough lines corresponding to the document edges are found, computing the document corners means to correctly intersect the lines. They are ordered based on theta, so that parallel lines are near each other, then the intersections between alternated lines are computed. In particular, the intersection using polar is calculated as follow:

@@

The implementation to find the intersection relies on \footnote{ numpy.linalg.solve: https://docs.scipy.org/doc/numpy/reference/generated/numpy.linalg.solve.html} which may raises an exception if the A matrix is singular because the computation is not possible. Whenever this happens, a least square solution, if it converges, via \footnote{numpy.linalg.lstsq: https://docs.scipy.org/doc/numpy/reference/generated/numpy.linalg.lstsq.html} is provided.

@@

\begin{figure}[H]
	\makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{computingcorners.png}}
	\caption{TODO}
	\label{fig:computingcorners}
\end{figure}

@@

\begin{figure}[H]
	\makebox[\textwidth][c]{\includegraphics[width=1\textwidth]{Warping.png}}
	\caption{TODO}
	\label{fig:warping}
\end{figure}

@@

The KODA implementation (shown in Fig. \ref{fig:keywordhighliting}) relies on this concept, but actually transforms each bounding box instead of the entire final overlay. Transforming the warped image copy (final overlay) would leads to black pixels all over the areas the document is not present, so that adding to the original image results to darken areas outside the document. To maintain intact these areas, the highlights are drawn directly on the original image copy (not warped) after they are transformed correctly. Granted that further operations to avoid the darkened areas are possible, the KODA implementation was chosen because it does not introduce additional overhead.

@@

\begin{figure}[H]
	\makebox[\textwidth][c]{\includegraphics[width=1.5\textwidth]{Highlighting.png}}
	\caption{ Examples of the keyword “on” highlighting. Note: the keyword is not searched as a perfect match, but as a substring of actual words. The highlight is applied to the entire word.}
	\label{fig:keywordhighliting2}
\end{figure}

>>>>

\begin{abstract}
This paper proposes a pipeline, KODA, suitable for keyword highlighting in document images. At its core, KODA uses a combination of edge detection, hough transform, OCR and warping to achieve the result. The study describes the custom, deep learning-based, approach for edge detection, motivated by the problems of traditional techniques and explaining the model training process, along with examples. Moreover, document detection and warping algorithms are detailed, as well as the keyword highlighting process.
\end{abstract}

\begingroup\let\clearpage\relax
\vspace{2cm}
\tableofcontents \endgroup

@@

The process is divided into two macro tasks (Fig. \ref{fig:pipeline}): image processing and keywords detection: The former detects a document from an image and retrieve all the contained words. The latter find user specified keywords, highlighting them in the document image.

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.8\linewidth]{Pipeline.png}
	\caption{KODA Pipeline scheme with sub-tasks. The computationally expensive processing is done once per input image, then the user can search for keywords and retrieves the output image multiple times repeatedly.}
	\label{fig:pipeline}
\end{figure}

\begin{figure}[!htbp]
	\includegraphics[width=\linewidth]{ipt.png}
	\caption{Image processing tasks example. Note: edges detection returns a resized image (256x256)}
	\label{fig:imageprocessing}
\end{figure}

@@

\subsection{First attempts with Canny}

@@

\subsection{Deep Learning approach}

@@

\subsection{Comparison between the two approaches}

@@

Once a set of lines is found, a sub-task is responsible to select the four best ones, one per each document edge. This is accomplished exploiting the fact that the Hough lines returned by the OpenCV interface are ordered by confidence: the first four strongest ones are selected, as shown in Fig. \ref{fig:hough}.

\begin{figure}[H]
	\makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{Hough.png}}
	\caption{Hough lines computation extracting the best one per each document edge.}
	\label{fig:hough}
\end{figure}

@@

Once the four Hough lines corresponding to the document edges are found, computing the document corners means to correctly intersect the lines. In order to distinguish lines that will be intersected from the others, they are sorted based on theta, so parallel lines are sequentially near to each other. In particular, the intersection is calculated as follow:

@@

The implementation to find the intersection relies on \footnote{ \texttt{numpy.linalg.solve}: https://docs.scipy.org/doc/numpy/reference/generated/numpy.linalg.solve.html} which may raises an exception if the A matrix is singular because the computation is not possible. Whenever this happens, a least square solution, if it converges, via \footnote{\texttt{numpy.linalg.lstsq}: https://docs.scipy.org/doc/numpy/reference/generated/numpy.linalg.lstsq.html} is provided.

@@

\begin{figure}[H]
	\makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{computingcorners.png}}
	\caption{Computing corners as intersections of extracted Hough lines.}
	\label{fig:computingcorners}
\end{figure}

@@

\begin{figure}[H]
	\makebox[\textwidth][c]{\includegraphics[width=1\textwidth]{Warping.png}}
	\caption{Comparison between original and warped images.}
	\label{fig:warping}
\end{figure}

@@

The KODA implementation (shown in Fig. \ref{fig:keywordhighliting}) relies on this concept, but actually transforms each bounding box instead of the entire final overlay. Transforming the warped image copy (final overlay) would lead to black pixels all over the areas where the document is not present: adding it to the orginal images results in darken areas outside the document. To avoid this problem, the highlights are drawn directly on the original image copy (not warped) after they are transformed correctly.

@@

\begin{figure}[H]
	\makebox[\textwidth][c]{\includegraphics[width=1.5\textwidth]{Highlighting.png}}
	\caption{ Examples of the keyword "on" highlighting. Note: the keyword is not searched as a perfect match, but as a substring of actual words. The highlight is applied to the entire word.}
	\label{fig:keywordhighliting2}
\end{figure}
